Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

\medskip
Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids. \citet{muskat_1934} investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
\begin{equation}
N_{c} = \frac{\mu U}{\gamma}.
\label{eq:capillary_number}
\end{equation}
In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface. This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.   
%The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law) since the Hele-Shaw apparatus may be used for both porous and non-porous media.  
More recently, \citet{howison_2000} and \citet{praud_2005} gave a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem). For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number. Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.

>>>>

\medskip
Viscous flow instabilities can be found across several disciplines and scales, from chemical separation processes to geological reservoir fluids. \citet{muskat_1934} investigated fluid flow in Hele-Shaw cells, \ie parallel flat plates separated by an infinitesimal gap, and the impact on the capillary number ($N_{c}$),
\begin{equation}
N_{c} = \frac{\mu U}{\gamma}.
\label{eq:capillary_number}
\end{equation}
In Eqn.~\ref{eq:capillary_number}, $\gamma$ is the surface tension and $U$ is the characteristic velocity of the moving interface. This experimental apparatus enables instabilities to be qualitatively investigated by simplifying the flow in both porous and non-porous media into a 2D problem.

More recently, \citet{howison_2000} and \citet{praud_2005} provided a comprehensive description of the mathematical formulation of immiscible two-phase flows in Hele-Shaw cells (also know as Saffman $\&$ Taylor problem). For a Hele-Shaw cell of a given size the developing flow only depends on the capillary number. Thus if \textit{$N_{c}$} is too high \citet{saffman_1959}, \citet{homsy_1987} and \citet{tabeling_1987} agreed that the flow develops into a single steady-state finger which moves through the cell with constant velocity $U$.
